### 2021-10-18 about/vita.tex
New post and slight revamp
Typos
Added paper
RSA

@@

\pubbegin P
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}, 11~pp.
To appear in {\sl Integers: Electronic Journal of Combinatorial Number Theory}, 2021.

@@

\begingroup\parindent=10pt
\thing (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl arXiv preprint 2007.05681}, 20~pp.
\thing (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}, 11~pp.
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 8~pp.
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\endgroup

\sectheader{Reports}

@@

\leftright{\bf First responder}{\bf October 2017 -- present}
\leftright{\sl McGill Student Emergency Response Team}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attend team training sessions twice a month to keep
first-aid skills up-to-date. Most recent first responder certification: September 2021.
\medbreak

>>>>

\sectheader{Graduate Coursework}

Higher algebra (categories, groups, modules), functional analysis, quadratic and modular forms, combinatorics.

@@

\pubbegin P
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 20~pp.
[arXiv 2007.05681]

@@

\begingroup\parindent=10pt
\smallskip
\thing (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}, 11~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 15~pp.
\smallskip
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\endgroup

\goodbreak
\sectheader{Reports}

@@

\leftright{\bf First responder}{\bf October 2017 -- present}
\leftright{\sl McGill Student Emergency Response Team}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attend team training sessions twice a month to keep
first-aid skills up-to-date. Most recent first responder certification: September 2020.
\medbreak
